\documentclass[a4paper,11pt,fleqn]{article}
%\usepackage{showkeys}
%\usepackage{refcheck}%check unused refs if showkeys activated
\usepackage{cite}
\usepackage{amsmath,mathtools}
\usepackage{amssymb}
%-----------
%\usepackage[usenames,dvipsnames]{pstricks}
%\usepackage{pstricks-add}
%\usepackage{pst-grad}
%\usepackage{pst-plot}
%\usepackage{pst-eucl}
%\psset{algebraic}
%--------
\usepackage{tikz}
\usepackage{pgfplots}
\usepackage{makeidx}
%\pgfplotsset{compat=1.15}
\usepackage{mathrsfs}
\usetikzlibrary{arrows}
\definecolor{ffwwqq}{rgb}{1.,0.4,0.}
\definecolor{qqzzqq}{rgb}{0.,0.6,0.}
\definecolor{qqqqff}{rgb}{0.,0.,1.}
\definecolor{dred}{HTML}{D90404}
\definecolor{orng}{HTML}{D35400}
\newcommand{\auth}[1]{{\color{dred} #1}}
\newcommand{\dft}{\ensuremath{\operatorname{DFT}}\,}

\usepackage{amssymb}
\usepackage{mathrsfs} 
\usepackage{theorem} 
\usepackage{booktabs}
\usepackage{euscript}
\usepackage{exscale,relsize}
\usepackage{graphicx}
\usepackage{booktabs}
\usepackage{srcltx}
\usepackage{xcolor}
\usepackage{charter}
\usepackage{pifont}
%\usepackage{mathabx}
%\usepackage{ntheorem}
%\usepackage[T1]{fontenc}
%\usepackage[bitstream-charter]{mathdesign}
\usepackage{url}

\newcommand{\email}[1]{\href{mailto:#1}{\nolinkurl{#1}}}
%------------------------------------------------------------------
\topmargin-0.0cm
\oddsidemargin -0.0cm
\textwidth16.5cm 
\headheight0.0cm
\textheight21.3cm
\parindent6mm
\parskip9pt
\tolerance1000
%\usepackage{amsthm}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{amsmath,color}
\setlength\parindent{15pt} % for paragraph alignment
\usepackage{wasysym}
\usepackage{amssymb}
\usepackage{epstopdf}
\usepackage{float}
\usepackage{mathrsfs}
%\usepackage{subfig}
\usetikzlibrary{arrows}
\definecolor{xdxdff}{rgb}{0.6588235294117647,
0.6588235294117647,0.6588}
\definecolor{qqqqff}{rgb}{0.3333333333333333,
0.3333333333333333,0.3333}
\DeclareCaptionFormat{cont}{#1 (cont.)#2#3\par}

%\usepackage[usenames,dvipsnames]{xcolor}
%\date{}
%\newtheorem{theorem}{Theorem}[section]
%\newtheorem{corollary}[theorem]{Corollary}
%\newtheorem{proposition}[theorem]{Proposition}
%\newtheorem{lemma}[theorem]{Lemma}
%\newtheorem{example}[theorem]{Example}
%\newtheorem{notation}[theorem]{Notation}
%\newtheorem{definition}[theorem]{Definition}
%\newtheorem{condition}[theorem]{Condition}
%\newtheorem{algorithm}[theorem]{Algorithm}
%\newtheorem{remark}[theorem]{Remark}
%\newtheorem{problem}[theorem]{Problem}
%\newtheorem{conjecture}[theorem]{Conjecture}
%\newtheorem{question}[theorem]{Question}
\newcommand{\vertiii}[1]{{\left\vert\kern-0.25ex\left\vert
\kern-0.25ex\left\vert #1 
\right\vert\kern-0.25ex\right\vert\kern-0.25ex
\right\vert}}
\newtheorem{theorem}{Theorem}[section]
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{corollary}[theorem]{Corollary}
\newtheorem{question}[theorem]{Question}
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{assumption}[theorem]{Assumption}
\theoremstyle{plain}{\theorembodyfont{\rmfamily}%
\newtheorem{conjecture}[theorem]{Conjecture}}
\theoremstyle{plain}{\theorembodyfont{\rmfamily}%
\newtheorem{example}[theorem]{Example}}
\theoremstyle{plain}{\theorembodyfont{\rmfamily}%
\newtheorem{remark}[theorem]{Remark}}
\theoremstyle{plain}{\theorembodyfont{\rmfamily}%
\newtheorem{algorithm}[theorem]{Algorithm}}
\theoremstyle{plain}{\theorembodyfont{\rmfamily}%
\newtheorem{condition}[theorem]{Condition}}
\theoremstyle{plain}{\theorembodyfont{\rmfamily}%
\newtheorem{definition}[theorem]{Definition}}
\theoremstyle{plain}{\theorembodyfont{\rmfamily}
\newtheorem{fact}[theorem]{Fact}}
\theoremstyle{plain}{\theorembodyfont{\rmfamily}
\newtheorem{problem}[theorem]{Problem}}
\theoremstyle{plain}{\theorembodyfont{\rmfamily}
\newtheorem{notation}[theorem]{Notation}}
\theoremstyle{plain}{\theorembodyfont{\rmfamily}
\newtheorem{project}[theorem]{Project}}
\def\proof{{\it Proof}. \ignorespaces}
\def\endproof{\vbox{\hrule height0.6pt\hbox{\vrule height1.3ex% 
width0.6pt\hskip0.8ex\vrule width0.6pt}\hrule
height0.6pt}}
\renewcommand\theenumi{(\roman{enumi})}
\renewcommand\theenumii{(\alph{enumii})}
\renewcommand{\labelenumi}{\rm (\roman{enumi})}
\renewcommand{\labelenumii}{\rm (\alph{enumii})}
\newcommand{\cone}{\ensuremath{\text{\rm cone}\,}}
\newcommand{\spts}{\ensuremath{\text{\rm{spts}\,}}}
\newcommand{\Fix}{\ensuremath{\text{\rm Fix}\,}}
\newcommand{\sign}{\ensuremath{\text{\rm sign}\,}}
\newcommand{\spa}{\ensuremath{\text{span}\,}}
\newcommand{\soft}[1]{\ensuremath{{\operatorname{soft}}_{{#1}}\,}}
\newcommand{\hard}[1]{\ensuremath{{\operatorname{hard}}_{{#1}}\,}}
\newcommand{\Argmin}{\ensuremath{{\text{\rm Argmin}}}}
\newcommand{\Scal}[2]{\bigg\langle{#1}\;\bigg|\:{#2}\bigg\rangle}
\newcommand{\scal}[2]{{\langle{{#1}\mid{#2}}\rangle}}
\newcommand{\sscal}[2]{{\big\langle{{#1}\mid{#2}}\big\rangle}}
\newcommand{\abscal}[2]{\left|\left\langle{{#1}\mid{#2}}}%
\newcommand{\emp}{\ensuremath{{\varnothing}}}
\newcommand{\minimize}[2]{\ensuremath{\underset{\substack{{#1}}}%
{\text{minimize}}\;\;#2 }}
%\numberwithin{equation}{section}
\setlength{\itemsep}{1pt} 


%-------------------------------- HYPERLINKS -------------------
%http://tug.ctan.org/cgi-bin/ctanPackageInformation.py?id=hyperref
\definecolor{labelkey}{rgb}{0,0.08,0.45}
\definecolor{refkey}{rgb}{0,0.6,0.0}
\definecolor{Brown}{rgb}{0.45,0.0,0.05}
\definecolor{dgreen}{rgb}{0.00,0.49,0.00}
\definecolor{dblue}{rgb}{0,0.08,0.75}
\RequirePackage[,colorlinks,hyperindex]{hyperref} %omitted dvips here
\hypersetup{linktocpage=true,citecolor=dblue,linkcolor=dgreen}
%--------------------------------------------------------------------
%Command \theoremstyle already defined. }
%Package natbib Error: Bibliography not compatible with author-year 
%citations. ...and\NAT@force@numbers{}\NAT@force@numbers
\usepackage{natbib}
\setlength{\bibsep}{3.5pt}
\def\HH{\mathcal H}
\def\BHG{\mathcal {B}(\mathcal{H},\mathcal{G})}
\def\card{\textnormal{card}}
\def\GG{\mathcal G}
\def\KK{\mathcal K}
\def\G0{\Gamma_0(\mathcal G)}
\def\H0{\Gamma_0(\mathcal H)}
\newcommand{\NN}{\ensuremath{\mathbb N}}
\newcommand{\RR}{\ensuremath{\mathbb{R}}}
\newcommand{\iin}{\ensuremath{\textrm{i}(n)}}
\newcommand{\ii}{\ensuremath{\textrm{i}}}
\newcommand{\RP}{\ensuremath{\left[0,+\infty\right[}}
\newcommand{\RM}{\ensuremath{\left]-\infty,0\right]}}
\newcommand{\RMM}{\ensuremath{\left]-\infty,0\right[}}
\newcommand{\BL}{\ensuremath{\EuScript B}\,}
\newcommand{\RPP}{\ensuremath{\left]0,+\infty\right[}}
\newcommand{\RPPX}{\ensuremath{\left]0,+\infty\right]}}
\newcommand{\ran}{\ensuremath{\text{\rm ran}\,}}
%\newcommand{\span}{\ensuremath{\text{\rm span}\,}}
\def\sri{\textnormal{sri}}
\newcommand{\reli}{\ensuremath{\text{\rm ri}\,}}
\newcommand{\pushfwd}{\ensuremath{\mbox{\Large$\,\triangleright\,$}
}}
%\def\Id{\text{Id}}
\newcommand{\menge}[2]{\big\{{#1}~\big |~{#2}\big\}}
\newcommand{\Menge}[2]{\left\{{#1}~\left|~{#2}\right.\right\}}

\newcommand*{\Id}{\text{\normalfont Id}}
\usepackage{lipsum}
\setcitestyle{square,citesep={,}}
\newcommand\scalemath[2]{\scalebox{#1}{\mbox{\ensuremath
{\displaystyle #2}}}}
\newcommand{\dom}{\ensuremath{\text{\rm dom}\,}}
\newcommand{\ri}{\ensuremath{\text{\rm ri}\,}}
\newcommand{\bdry}{\ensuremath{\text{\rm bdry}\,}}
\newcommand{\Int}{\ensuremath{\text{\rm int}\,}}
\newcommand{\supp}{\ensuremath{\text{\rm supp}\,}}
\newcommand{\gra}{\ensuremath{\text{\rm gra}\,}}
\newcommand{\prox}{\ensuremath{\text{\rm Prox}\,}}
\newcommand{\zer}{\ensuremath{\text{\rm zer}\,}}
\newcommand{\rec}{\ensuremath{\text{\rm rec}\,}}
\newcommand{\core}{\ensuremath{\text{\rm core}}}
\newcommand{\range}{\ensuremath{\text{\rm range}\,}}
\usepackage{lineno,hyperref}
\modulolinenumbers[5]

\bibliographystyle{elsarticle-num}


\begin{document}
\title{``Daily-Log of Internship at ZIB"}
\author{Utkarsh Sharma}
\date{22/5/23 - present}
\maketitle 
\begin{itemize}
\item {\bf May 22, 2023}: 
\begin{itemize} 
\item Started with Class on Prox methods and non-smooth convex optimization
\item Installed Julia locally and learnt its basic syntax
\item Submitted Homework exercises pertaining to Lecture-1
\end{itemize}
\item {\bf May 23, 2023}:
\begin{itemize} 
\item Read \cite{drusvyatskiy_proximal} sections 1 - 3
\item Went through class Lecture-2 and Lecture-3's notes and completed their exercises
\item Read \cite{Johnstone2020projective} pages 1-10, with special attention to the assumptions listed and Algorithm - 1
\end{itemize}

\item {\bf May 24, 2023}:
\begin{itemize} 
\item Went through Lecture 4's notes and completed the exercises
\item Went through \textit{Mert Pilanci (Stanford University) - Monotone Operators} to understand maximal monotone operators and related stuff overlapping with \cite{Johnstone2020projective}
\end{itemize}

\item {\bf May 25, 2023}:
\begin{itemize} 
\item Read \textit{S. Boyd, J. Duchi, M. Pilanci, and L. Vandenberghe - Subgradients} lecture notes to understand some properties of subgradients
\item Continued reading about \cite{Johnstone2020projective} and tried to build an intuition towards Algorithm-2
\item Went through Lecture Notes 5 of Crash Course
\item Homework Exercises pertaining to today's lecture
\end{itemize}

\item {\bf May 26, 2023}:
\begin{itemize} 
\item Watched \textit{Gilbert Strang - Singular Value Decomposition} to learn about SVD and its mention in the class notes
\item Went through the notes of the last lecture
\item Homework Exercises for the last lecture
\item Installed Julia in the Z1 cluster of ZIB
\end{itemize}

\item {\bf May 30, 2023}:
\begin{itemize} 
\item Meeting with my Advisor wherein he explained the intuition of Algorithms in \cite{PCombetteEckstein} and some other technical details.
\item Read and tried to understand the hierarchy of last year's project code for Algorithm-4 mentioned in \cite{PCombetteEckstein}
\item Analysed different functions under AsyncProx/Comb18 Library
\end{itemize}

\item {\bf May 31, 2023}:
\begin{itemize} 
\item Collaborated with my project partner to go over last year's repository and find out missing elements, features and design decisions in it.
\end{itemize}

\item {\bf June 1, 2023}:
\begin{itemize} 
\item Wrote the default algorithm for choosing blocks $I_n$ - in a cyclic manner. Also added the functions so that the user can choose any block-choosing strategy function of their own and use it in the code.
\item Ran the previous algorithm on a bunch of different settings to further understand its limitations and structure.
\end{itemize}

\item {\bf June 2, 2023}:
\begin{itemize} 
\item Discussed with my project partner what changes we should make in the current code to make it better.
\item Meet with Aryan Dua, where he explained Comb18 directory's code - what are its limitations, design decisions, reasons for the design choices made.
\end{itemize}

\item {\bf June 5, 2023}:
\begin{itemize} 
\item Studied @tasks in Julia (https://docs.julialang.org/en/v1/base/parallel/) to understand the syntax and rules for asynchronous programming in Julia.
\item Wrote the algorithm for the `indices not inside block $I_n$' and added choosing a generic or specific block option in the code.
\end{itemize}

\item {\bf June 6, 2023}:
\begin{itemize} 
\item Meet with our advisor about bugs found in previous code, changes and design decisions for generalising it to n-dimensions
\item made a list of dimension sizes for each matrix in the code so as to fit the matrix products correctly for generalised dimensions
\end{itemize}

\item {\bf June 7, 2023}:
\begin{itemize} 
\item Worked with my project partner to fix bugs and write the code further
\item Came up with two optimisation problems for testing:
\begin{itemize}
  \item For 2 dimensions with an added indicator for projecting the domain onto the diagonal subspace
  \item For 3 dimensions - that can be worked out by hand
\end{itemize}
\end{itemize}

\item {\bf June 9, 2023}:
\begin{itemize} 
\item Tested the code for a 3-dimensional optimisation problem - worked correctly
\item Implemented an optimisation problem for $m = 3$ and $p = 5$ where $\mathcal{H}_1 = \mathcal{H}_2 = \mathbb{R}^2$, $\mathcal{H}_3 = \mathbb{R}^3$, $\mathscr{G}_1 = \mathscr{G}_2 = \mathscr{G}_3 = \mathscr{G}_4 = \mathbb{R}^2$ and $\mathscr{G}_5 = \mathbb{R}^3$. 
\item Calculated the required answer for the above problem manually and compared it with the code to see that it matches.
\item Implemented matrix $L$ and more required functions so that functions $g_k$ can now accept linear combinations of \textit{transformations} of $x_i$ rather than just linear combinations of $x_i$ as previously.
\end{itemize}

\item {\bf June 12, 2023}:
\begin{itemize} 
\item With my project partner, tested another optimisation problem in 3-dimensions to see that it works correctly.
\item Fixed a bug in the default block generating function and tested problems with different parameters of block generation.
\item Ensured that lags are no longer than $M$ in the default strategy, where $M$ can be adjusted in the cyclic block selection function.
\end{itemize}

\item {\bf June 13, 2023}:
\begin{itemize} 
\item Tested the optimisation problem for new simple problems to ensure completeness.
\end{itemize}

\item {\bf June 14, 2023}:
\begin{itemize} 
\item Implementation of $\gamma_n$ and $\mu_n$ sequences to be fed into the program as a function by the user.
\end{itemize}

\item {\bf June 15, 2023}:
\begin{itemize} 
\item Ran testcases where there was either no solution (an empty domain)  
\end{itemize}

\item {\bf June 15, 2023}:
\begin{itemize} 
\item Ran testcases where there was no solution (an empty intersection of all domains).
\item Ran a testcase where the function $g$ accepts a linear combination of transformed variables $x_i$ of different dimensions.
\end{itemize}

\item {\bf June 16, 2023}:
\begin{itemize} 
\item Changed the code structure to now accept $L$ as a matrix of functions.
\item For $L^*$, the user would input the adjoint functions as a matrix. 
\item Created the option for a boolean variable that selects whether the user wants to use $L$ as a matrix of functions or as a matrix of matrix transformations.
\end{itemize}


\item {\bf June 19, 2023}:
\begin{itemize} 
\item Spent much of the time reading \cite{ImageCompressionHussain} to learn about different Image Compression Techniques.
\end{itemize}

\item {\bf June 20, 2023}:
\begin{itemize} 
\item Continued reading \cite{ImageCompressionHussain}
\item Meet with my advisor discussing the results for different $\gamma_n$ and $\mu_n$ strategies and regarding the example problem for image recovery.
\end{itemize}

\item {\bf June 21, 2023}:
\begin{itemize} 
\item Read about the different kinds of wavelet bases and their functions.
\item Read \cite{ImageRecoveryPCombettes} with special attention to 5.1.1 i.e. our example problem for spectroscopic image recovery.
\item 
\end{itemize}

\end{itemize}

\bibliographystyle{plain}
\bibliography{ref}
\end{document}
